% !TEX root = ../../teaching_online.tex
\newpage
\section{Syracuse University Expressions}

% What is Expressions
\subsection{What is Expressions}

Expressions is a Syracuse University hosted WordPress account. It is the equivalent of a premium account of WordPress. This allows you to make a site, upload a theme, and start building your own website. You can use this to host class page(s), as a teaching portfolio, blog site, etc. For instance, you are able to build a site like the one found here: \url{https://coffeeintotheorems.com/} or \url{https://jjheffer.expressions.syr.edu/}. These pages are also the basis for many university pages and you can set one up for your graduate department. For instance, \url{http://mgo.syr.edu/} is a university hosted Expressions page. 



% Signing Up
\subsection{Signing Up}

Each student and faculty can create their own WordPress site for free. Currently, you are able to keep the page even after you leave Syracuse University. The only difference between this and a typical WordPress premium page is that the page will have a \its{.expressions.syr.edu} url and some plugins may conflict with the University hosting. Signing up for an Expressions page is easy! Simply follow the link below and sign-up using your university NetID and password.

	\begin{itemize}
	\item Expressions at Syracuse University: \url{https://expressions.syr.edu/}
	\end{itemize}


% How to Use
\subsection{How to Use Expressions}

We will not go into details on how to navigate using WordPress. There is a lot of literature out there on the internet on using WordPress. Syracuse University also has a help resource page for Expressions at Syracuse University. 

	\begin{itemize}
	\item Syracuse Expressions Help Page: \url{https://answers.syr.edu/display/ITHELP/Expressions}
	\end{itemize}

Individual sites have up to 2~GB of storage while faculty sites for academic purposes host up to 5~GB. Of course, you can instead add links on your page to a Google Drive, DropBox file, etc rather than uploading the file directly to the Expressions system to help extend this storage. Below are a few links specific to the Syracuse University Expressions system. Of course, you may feel free to email IT with questions about Expressions. If your site ever goes down (which often happens if there are plugin conflicts), you may email IT to help bring the site back up.

	\begin{itemize}
	\item Expressions FAQ: \url{https://answers.syr.edu/display/ITHELP/Expressions+Frequently+Asked+Questions}
	\item Using Expressions: \url{https://answers.syr.edu/display/ITHELP/How+to+Use+Expressions}
	\item Syracuse University IT Help Page: \url{https://its.syr.edu/get-help/}
	\end{itemize}





% Advice
%\subsection{Expressions Advice}





















